%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tutorial
% LaTeX Template
% Version 1.0 (05/11/17)
%
% Remix author:
% Ben Roose (ben.roose@wichita.edu)
%
% Original temlate author:
% Adam Glesser (adamglesser@gmail.com)
% www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry} % Required to make the margins smaller to fit more content on each page
\usepackage[linkcolor=blue]{hyperref} % Required to create hyperlinks to questions from elsewhere in the document
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue} % Specify a color for hyperlinks
\usepackage{todonotes} % Required for the boxes that questions appear in
\usepackage{tocloft} % Required to give customize the table of contents to display questions
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{palatino} % Use the Palatino font

\setlength\parindent{0pt} % Removes all indentation from paragraphs

% Create and define the list of questions
\newlistof{questions}{faq}{\large List of Frequently Asked Questions} % This creates a new table of contents-like environment that will output a file with extension .faq
\setlength\cftbeforefaqtitleskip{4em} % Adjusts the vertical space between the title and subtitle
\setlength\cftafterfaqtitleskip{1em} % Adjusts the vertical space between the subtitle and the first question
\setlength\cftparskip{.3em} % Adjusts the vertical space between questions in the list of questions

% Create the command used for questions
\newcommand{\question}[1] % This is what you will use to create a new question
{
\refstepcounter{questions} % Increases the questions counter, this can be referenced anywhere with \thequestions
\par\noindent % Creates a new unindented paragraph
\phantomsection % Needed for hyperref compatibility with the \addcontensline command
\addcontentsline{faq}{questions}{#1} % Adds the question to the list of questions
\todo[inline, color=green!40]{\textbf{#1}} % Uses the todonotes package to create a fancy box to put the question
\vspace{1em} % White space after the question before the start of the answer
}

% Uncomment the line below to get rid of the trailing dots in the table of contents
%\renewcommand{\cftdot}{}

% Uncomment the two lines below to get rid of the numbers in the table of contents
%\let\Contentsline\contentsline
%\renewcommand\contentsline[3]{\Contentsline{#1}{#2}{}}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND LIST OF QUESTIONS
%----------------------------------------------------------------------------------------

\begin{center}
\Huge{\bf \emph{EECS Tutorial: Accessing the Routing \& Switching Lab}} % Main title
\end{center}

\listofquestions % This prints the subtitle and a list of all of your questions

\newpage % Comment this if you would like your questions and answers to start immediately after table of questions

%----------------------------------------------------------------------------------------
%	QUESTIONS AND ANSWERS
%----------------------------------------------------------------------------------------

\question{How do I access rslab equipment from a mobile Linux GUI terminal in EE 328C/D?}\label{Mobile Linux Terminals}

\begin{enumerate}
\item In EE 327C turn on a mobile Linux PC. PC will network boot from the LTSP server and automatically login.
\item Open \textit{PAC Manager} from the desktop or \textit{applications} menu.
\item On  left side, double-click the terminal server for the rack \# assigned to you by GTA.
\item Once connected to the terminal server for your assigned rack, use the menu options to access the Arista swiches and Cisco router in the EE 328D networking rack.
\item To return to the terminal server menu by pressing \texttt{CTRL+SHIFT+7} at any time.
\item To exit from the terminal server, return to the menu and press \texttt{18}.
\end{enumerate}
\textbf{NOTE:} You can open multiple tabbed windows to access the same terminal server from within \textit{PAC Manager}.
[BEN: ADD SCREENSHOT OF PAC MANAGER]


%------------------------------------------------

\question{How do I access rslab equipment from a Windows, Linux, or Mac PC outside of EE 328C/D?}\label{Mobile Linux Terminals}

\begin{enumerate}
\item Due to network security, you will need to use one of the EECS Linux servers as an SSH proxy.
\item Follow the \textit{Remote Access EECS Linux Servers.pdf} document first to log into an EECS Linux Server.
\item Once logged into an EECS Linux server, use SSH to access rslab proxy server, by typing:
\begin{verbatim}
ssh -t rslab telnet rack#
\end{verbatim}
where \texttt{\#} is the rack number assigned to you by GTA (adding ssh option \texttt{-t} is recommended)
\item Enter your myWSU password when prompted to do so.
\item Once connected to the terminal server for your assigned rack, use the menu options to access the Arista swiches and Cisco router in the EE 328D networking rack.
\item To return to the terminal server menu by pressing \texttt{CTRL+SHIFT+6} and then \texttt{x} at any time.
\item To exit from the terminal server, return to the menu and press \texttt{18}.
\end{enumerate}
\textbf{NOTE:} You can open multiple command-line/shell windows from your client machine to access the same terminal server, or you can use a terminal multiplexer such as \textit{screen} or \textit{tmux} within any of the EECS Linux servers.
[BEN: ADD SCREENSHOT OF ssh rslab in a terminal]


%------------------------------------------------
\question{Why is there a label in the code for \hyperref[new-question]{the previous question}?}\label{labels}

This is not necessary, but it does give you a way of linking to a different question. In order to link to another question you simply need to add the following:

\begin{verbatim}
\hyperref[question-label]{click here}
\end{verbatim}

The first part \texttt{[question-label]} is the label name and the second part \texttt{\{click here\}} is the text that is displayed as link.

%------------------------------------------------

\question{How do I change the title and subtitle?}\label{change-title}

To change the main title, simply find the "TITLE AND LIST OF QUESTIONS" block and replace "A Template for FAQ's" within it. To change the subtitle find the following command:

\begin{verbatim}
\newlistof{questions}{faq}{\large List of Frequently Asked Questions}
\end{verbatim}

and replace the subtitle with one of your choosing.

%------------------------------------------------

\question{Is it possible to change the spacing between the questions in the list of questions?}\label{change-spacing}

Yes, simply find the following line:

\begin{verbatim}
\setlength\cftparskip{.3em}
\end{verbatim}

and change the \texttt{.3em} to whatever suits your fancy.

%------------------------------------------------

\question{What if I want to hide the page numbers and/or trailing dots next to the question in the list of questions?}\label{page-numbering}

To remove the trailing dots to the page numbers, find the line:

\begin{verbatim}
%\renewcommand{\cftdot}{}
\end{verbatim}
and uncomment it. To remove the page numbers as well, find the following lines and uncomment them:
\begin{verbatim}
%\let\Contentsline\contentsline
%\renewcommand\contentsline[3]{\Contentsline{#1}{#2}{}}
\end{verbatim}

%------------------------------------------------

\question{Is it possible to number questions?}\label{number-questions}

Yes, you can refer to the number of the current question with:

\begin{verbatim}
\thequestions
\end{verbatim}
 
For example, this is question \thequestions. You can even incorporate question numbers into the questions and list of questions automatically by adding:

\begin{verbatim}
Question \thequestions:
\end{verbatim}

just before each \texttt{\#1} in the \texttt{\textbackslash questions} definition block in the preamble.

%------------------------------------------------

\question{Question \thequestions: Can I change the color of the question boxes?}\label{question-color}

Just find the following line and change the color specified there:

\begin{verbatim}
\todo[inline, color=green!40]{\textbf{#1}}
\end{verbatim}

%----------------------------------------------------------------------------------------

\end{document}